Peer influences in air travel behavior: A social autoregressive analysis

### 2015-04-10 article/article.Rmd
Created graph and adjacency matrices from data.

library(dplyr, warn.conflicts = FALSE) # super data wrangling
library(igraph) # graph analysis
library(networkD3) # interactive graph visualizer
```

@@

```{r load_user}
trips <- readRDS("data/clean/trips.rds")
user <- readRDS("data/clean/user.rds")
friends <- readRDS("data/clean/friends.rds")
```

@@

```{r force_symmetric}
# still need to implement
```

@@

```{r save_as_matrices}

>>>>

library(dplyr, warn.conflicts = FALSE) # super data wrangling
library(tidyr)
library(igraph) # graph analysis
library(networkD3) # interactive graph visualizer
```

@@

```{r load_user, warning=FALSE}
source("../rscripts/datacleaner.R")
```

@@

```{r save_as_matrices}
# make graph
user_graph <- graph.data.frame(friend_connections)

# export graph edges as adjacency matrix
matrix_list <- list()
for(i in names(friend_connections)[-(1:2)]){
  matrix_list[[i]] <- get.adjacency(user_graph, type = "both", i)

  # TODO force symmetric
}
```

@@
